Instructions for developing new pages for the MarineOmics webpage

### 2023-12-14 DRAFT_DNA_methylation.Rmd
downstream

## Other application

-   Gene-level methylation analysis: people do this, but worth considering the utility of converting loci-level resolution data to gene-level resolution data
-   methylKit
-   IGV
-   Analysis with other datasets (ex. pop gen, RNA-Seq)

>>>>

## Downstream application

-   Gene-level methylation analysis. It is worth considering the utility of converting loci-level resolution data to gene-level resolution data

-   Differential loci or region analyses. methylKit is a popular package to conduct this analysis

-   Feature overlap. Bedtools for quantitative assessment and IGV for visual assessment are valuable for thisl
